Mapping out the punishment strategy space

### 2023-07-04 report.Rmd
add study 2 data

@@

We then fit a series of models predicting the usage of different strategies from a variety of predictors. In each plot that follows, we show the posterior predictions from a model that includes a single variable as a predictor of all ten strategies simultaneously. The plots show the median regression lines with shaded 95% credible intervals. The model-estimated slopes for each strategy are included in each panel.

```{r plot2, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_Age)
tar_read(plot2_SelfRate_1)
tar_read(plot2_SelfRate_2)
tar_read(plot2_SelfRate_3)
tar_read(plot2_SelfRate_4)
tar_read(plot2_SelfRate_5)
tar_read(plot2_SelfRate_6)
tar_read(plot2_SelfRate_7)
tar_read(plot2_SelfRate_8)
tar_read(plot2_SelfRate_9)
tar_read(plot2_SelfRate_10)
tar_read(plot2_SelfRate_11)
```

>>>>

\newpage

@@

We then fit a series of models predicting the usage of different strategies from a variety of predictors. In each plot that follows, we show the posterior predictions from a model that includes a single variable as a predictor of all ten strategies simultaneously. The plots show the median regression lines with shaded 95% credible intervals. For continuous predictors, the model-estimated slopes for each strategy are included in each panel.

## Demographics

We find that several demographic factors predict usage of the "anti-punish" strategy. Specifically, people who are white, male, higher educated (PhD-level), and students are more likely to follow the anti-punish strategy. Age and socio-economic status are unrelated to all strategies.

```{r plotPredDemographics, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_Age)
tar_read(plot3_Education)
tar_read(plot3_Ethnicity)
tar_read(plot3_Gender)
tar_read(plot2_SES)
tar_read(plot3_Student)
```

\newpage

## Self-ratings

Answers to the self-rating sliders were related to strategy usage in predictable ways. In general, citing any reason to punish tended to be negatively related to usage of the anti-punish strategy. People citing egalitarian, harm-reduction, or disapproval-signalling motivations were more likely to follow egalitarian and/or norm enforcing strategies. In addition:

- people who wanted to _have a higher final bonus than others_ or _avoid having a lower final bonus than others_ were more likely to follow the antisocial strategy
- people who admitted that they _decided at random_ were more likely to follow the random choice strategy
- people who _punishing those who did NOT cause harm_ were less likely to follow the egalitarian strategy and more likely to follow the avoid DI and random choice strategies

```{r plotPredSelfRate, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_SelfRate1)
tar_read(plot2_SelfRate2)
tar_read(plot2_SelfRate3)
tar_read(plot2_SelfRate4)
tar_read(plot2_SelfRate5)
tar_read(plot2_SelfRate6)
tar_read(plot2_SelfRate7)
tar_read(plot2_SelfRate8)
tar_read(plot2_SelfRate9)
tar_read(plot2_SelfRate10)
tar_read(plot2_SelfRate11)
```

\newpage

# Big-6 personality

Personality was largely unrelated to strategy usage. The only slopes with 95% credible intervals that excluded zero were for extraversion and honesty-humility. Extraversion negatively predicted usage of the anti-punish strategy, while honesty-humility positively predicted usage of the anti-punish strategy.

```{r plotPredPersonality, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_Agree)
tar_read(plot2_Consc)
tar_read(plot2_Extra)
tar_read(plot2_Honest)
tar_read(plot2_Neur)
tar_read(plot2_Open)
```

\newpage

# Social value orientation

We found that social value orientation angle positively predicted usage of the egalitarian and anti-punish strategies.

```{r plotPredSVO, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_SVOangle)
```

\newpage

# Political views

Political ideology was largely unrelated to strategy usage. Unidimensional political ideology was unrelated to all strategies, while SDO and RWA negatively predicted usage of the anti-punish strategy. Wanting to bring people up or down a peg on the SES ladder was also unrelated to strategy usage.

```{r plotPredPolIdeology, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_PolSlider)
tar_read(plot2_SDO)
tar_read(plot2_RWA)
tar_read(plot2_BringDown)
tar_read(plot2_BringUp)
```

\newpage

# Religion

Both religiosity items were unrelated to strategy usage.

```{r plotPredReligion, fig.width=7, fig.height=4, fig.align='center', out.width="100%"}
tar_read(plot2_Religiosity)
tar_read(plot2_GodC)
```
